%==============================================================
%  Curriculum Vitae -- Eonyong Han
%  Compile:  latexmk -pdf cv.tex   (or)   pdflatex cv.tex
%  Self-contained: uses only standard LaTeX packages.
%==============================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.2cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{ifthen}

\definecolor{accent}{HTML}{1A3A5A}
\hypersetup{colorlinks=true, linkcolor=accent, urlcolor=accent, citecolor=accent}

% ---- Section styling ---------------------------------------
\titleformat{\section}
  {\Large\bfseries\color{accent}}{}{0pt}{}[\vspace{-4pt}\color{accent}\hrule\vspace{2pt}]
\titlespacing{\section}{0pt}{12pt}{6pt}

% ---- Helper commands ---------------------------------------
% Entry with a right-aligned date
\newcommand{\entry}[2]{%
  \noindent\textbf{#1}\hfill{\color{accent}#2}\par}
\newcommand{\subentry}[1]{\noindent\textit{#1}\par}

% Highlight the CV owner's name wherever it appears in author lists
\newcommand{\me}[1]{\textbf{#1}}

\setlist[itemize]{leftmargin=1.4em, itemsep=2pt, topsep=3pt}

\newcommand{\namefont}{\Huge\bfseries\color{accent}}

%==============================================================
\begin{document}
\pagestyle{empty}

% ---------------- HEADER ------------------------------------
\begin{center}
  {\namefont Eonyong Han}\\[4pt]
  {\large Ph.D.\ Candidate, Bioinformatics \& Computational Biology}\\[2pt]
  School of Computer Science and Engineering, Kyungpook National University\\
  Buk-gu, Daegu 41566, Republic of Korea\\[6pt]
  % --- Contact line: EDIT placeholders below ---
  \href{mailto:djssoddl@knu.ac.kr}{djssoddl@knu.ac.kr}
  \quad\textbullet\quad
  +82-XX-XXXX-XXXX
  \quad\textbullet\quad
  \href{https://scholar.google.com/citations?user=NMRL9agAAAAJ}{Google Scholar}
  \quad\textbullet\quad
  \href{https://github.com/YOUR-GITHUB}{GitHub}
  \quad\textbullet\quad
  \href{https://orcid.org/0000-0000-0000-0000}{ORCID}
\end{center}
\vspace{4pt}

% ---------------- RESEARCH INTERESTS ------------------------
\section{Research Interests}
Multi-omics data integration; computational cancer genomics; machine learning for
biomedical data; transcriptomics and pathway analysis; immune-response modeling in
infectious disease (COVID-19). Emphasis on translating high-throughput sequencing
data into clinically interpretable insights.

% ---------------- EDUCATION ---------------------------------
\section{Education}
\entry{Ph.D.\ in Computer Science and Engineering}{20XX -- 2026 (expected)}
\subentry{Kyungpook National University, Daegu, Republic of Korea}
\begin{itemize}
  \item Dissertation: \emph{[Working title -- e.g., ``Multi-omics integration methods for cancer subtyping and disease-progression modeling'']}
  \item Advisor: Prof.\ Inuk Jung
\end{itemize}
\vspace{4pt}
\entry{[B.S. / M.S.]\ in [Field]}{20XX -- 20XX}
\subentry{[University], [City], Republic of Korea}

% ---------------- PUBLICATIONS ------------------------------
\section{Publications}
\noindent\footnotesize$^{\dagger}$Co-first author. Author's name in \textbf{bold}.
Full metadata in \texttt{references.bib}.\normalsize
\vspace{4pt}

\subentry{Peer-reviewed journal articles}
\begin{enumerate}[leftmargin=1.8em, itemsep=6pt, label=\arabic*.]
  \item \me{Han, E.}, Youn, S., Kwon, K.T., Kim, S.C., Jo, H.-Y., \& Jung, I. (2024).
        Disease progression associated cytokines in COVID-19 patients with deteriorating
        and recovering health conditions. \emph{Scientific Reports}, 14, 24712.
        \href{https://doi.org/10.1038/s41598-024-75924-x}{doi:10.1038/s41598-024-75924-x}

  \item \me{Han, E.}$^{\dagger}$, Kwon, H.$^{\dagger}$, \& Jung, I. (2025).
        A review on multi-omics integration for aiding study design of large scale TCGA
        cancer datasets. \emph{BMC Genomics}, 26, 769.
        \href{https://doi.org/10.1186/s12864-025-11925-y}{doi:10.1186/s12864-025-11925-y}

  \item Youn, S., Jeong, D., Kwon, H., \me{Han, E.}, Kim, S., \& Jung, I. (2025).
        Identification of severity related mutation hotspots in SARS-CoV-2 using a
        density-based clustering approach. \emph{BioData Mining}, 18, 61.
        \href{https://doi.org/10.1186/s13040-025-00476-3}{doi:10.1186/s13040-025-00476-3}

  \item Shin, S., \me{Han, E.}, Seong, H., Kim, Y.I., Jung, I., \& Jung, W. (2025).
        De novo transcriptome assembly and gene expression analysis of Cnidium officinale
        under high-temperature conditions. \emph{BMC Genomics}, 26, 907.
        \href{https://doi.org/10.1186/s12864-025-12051-5}{doi:10.1186/s12864-025-12051-5}

  \item Jeon, J., \me{Han, E.Y.}, \& Jung, I. (2023).
        MOPA: An integrative multi-omics pathway analysis method for measuring omics
        activity. \emph{PLOS ONE}, 18(3), e0278272.
        \href{https://doi.org/10.1371/journal.pone.0278272}{doi:10.1371/journal.pone.0278272}
\end{enumerate}

% ---------------- RESEARCH EXPERIENCE -----------------------
\section{Research Experience}
\entry{Graduate Researcher --- Computational Biology \& Bioinformatics Lab}{20XX -- Present}
\subentry{Kyungpook National University, Daegu}
\begin{itemize}
  \item Developed multi-omics integration and pathway-analysis methods for cancer
        subtyping using TCGA datasets (gene expression, miRNA, methylation).
  \item Built machine-learning models (random forest, SHAP-based interpretation) to
        characterize COVID-19 immune response from EHR and cytokine-profile cohorts.
  \item Applied density-based clustering to identify SARS-CoV-2 mutation hotspots
        associated with patient severity from large-scale genomic databases (GISAID).
\end{itemize}

% ---------------- SKILLS ------------------------------------
\section{Technical Skills}
\begin{itemize}
  \item \textbf{Programming:} [Python, R], [Bash]; \emph{add others you use}
  \item \textbf{Bioinformatics:} RNA-seq / DEG analysis, de novo transcriptome assembly,
        pathway \& GO/KEGG enrichment, multi-omics integration, single-cell RNA-seq
  \item \textbf{Machine learning:} clustering, random forests, SHAP / explainable AI,
        feature selection, benchmarking
  \item \textbf{Tools:} Git, [Linux/HPC], [add frameworks]
\end{itemize}

% ---------------- PRESENTATIONS / AWARDS / SERVICE ----------
\section{Presentations, Awards \& Service}
\begin{itemize}
  \item \emph{[Add conference talks / posters, e.g., name, venue, year.]}
  \item \emph{[Add scholarships, fellowships, or awards.]}
  \item \emph{[Add peer-review or academic service, if any.]}
\end{itemize}

% ---------------- REFERENCES --------------------------------
\section{References}
\entry{Prof.\ Inuk Jung}{Ph.D.\ Advisor}
\subentry{School of Computer Science and Engineering, Kyungpook National University}
\href{mailto:inukjung@knu.ac.kr}{inukjung@knu.ac.kr}
\vspace{4pt}

\noindent\emph{Additional references available upon request.}

\end{document}
